---
title: "dados_python"
format: html
editor: source
---

## Libraries

```{r}
library(tidyverse)
library(torch)
# torch::install_torch()

torch::install_torch()
usethis::edit_r_environ()
```

## Data

```{r}

load("/Volumes/GoogleDrive-103548588935465845166/Meu Drive/NLP_psicom/bfi/base_padrao.RData")
load("/Volumes/GoogleDrive/Meu Drive/NLP_psicom/bfi/base_padrao.RData")

save(db_textos, db_bfi, lexical, split_texts, slide_windows, nearest_neighbors, file = "../data/data_bfi_nlp.RData")

library(reticulate)
library(readxl)
base_itens <- read_excel("../data/base_itens.xlsx")

rm(builtins, file, pickle, reshaped_slices, slice, i, j, new_array, old_array, third_dim, x)
```

## Final data 
```{r}

load("~/Dropbox (Personal)/B5_NLP/colB5BERT/data/data_bfi_nlp.RData")
save.image("~/Dropbox (Personal)/B5_NLP/colB5BERT/data/data_bfi_nlp.RData")

library(readr)
db_textos_splitted <- read_delim("../data/db_textos.splitted.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)

```

```{r}
db_textos_splited <- split_texts(db_textos = db_textos, numero_palavras_por_divisao = 250)


View(db_textos_splitted)

db_splited_embeddings %>% group_by(id) %>%
 summarise(num_splits = max(id_divisao)) %>%
 ggplot(aes(x = num_splits)) + geom_histogram(color = "white")

db_textos_splitted  %>% group_by(id) %>%
 summarise(num_splits = max(id_divisao)) %>%
 ggplot(aes(x = num_splits)) + geom_histogram(color = "white") +
 scale_x_continuous(breaks = scales::breaks_pretty(20))

# write_csv2(db_textos_splited, file = "../data/db_textos.splitted.csv")

db_textos_splited %>% select(-texto) %>%
 write_csv2(file = "../data/db_textos.splitted.csv")

```

## Reading embeddings saved in numpy arrays

* In numpy npz file
```{r}
library(reticulate)

# Import numpy
np <- import("numpy")

# Use numpy's load function to open the .npz file

emb_posts <- np$load("/Volumes/GoogleDrive/Meu Drive/colB5BERT/embeddings_posts.npz", allow_pickle=TRUE)

# The data object is a Python dictionary. You can convert it to a list in R.
emb_itens <- py_to_r(emb_itens)
emb_posts <- py_to_r(emb_posts)

# Get a named array from the .npz file
emb_itens_L6 = emb_itens[['6']]
emb_posts_L6 = emb_posts[['6']][[1:4]]

glimpse(emb_itens_L6)

str(data)


```
* in pickle file .pkl
```{r}

# Import necessary modules
pickle <- import("pickle")
builtins <- import_builtins()

# Open the pickle file and load it
file <- builtins$open("cosim_scores_L6.pkl", "rb")
cosim_L6_scores <- pickle$load(file)

# Close the file after reading
file$close()


```



## Preparing metadata for analysis

```{r}

item_dims <- purrr::map_int(cosim_L6, ~dim(.x)[2])
length(array_dims) == length(cosim_L6)

table(array_dims)

third_dims <- purrr::map_int(cosim_L6, ~dim(.x)[3])

table(third_dims )

library(purrr)
library(rray)
install.packages(c( "rray"))
table(length_tokens_itens)

which(third_dims == 3, arr.ind = TRUE, useNames = TRUE)

cosim_L6[[8495]][1,,]

```


### Structurre of the data 

* cosim_L6 lista de 5 em 5 posts. É um array baths X tokens dos itens X  5 cosim max do post
* 5*length(cosim_L6) = 4.787.855
* this is a working solution but slow

```{r}

cosim_L6b <- matrix(nrow = 0, ncol = 7)

for (i in 1:length(cosim_L6)) {
  
 for (j in 1:5) {
  
  mat <- cosim_L6[[i]][j, , ]
 
  # Check the number of columns in the current matrix and base matrix
  num_cols_base <- 5
  num_cols_current <- ncol(mat)
  
  if (num_cols_base > num_cols_current) {
    # Add columns filled with NA to the current matrix
    mat <- cbind(mat, matrix(rep(NA, (num_cols_base - num_cols_current) * nrow(mat)), nrow=nrow(mat)))
  }
   cosim_L6b <- rbind(cosim_L6b, cbind(batch = i, n_in_batch = j, mat))
 }

 }


```

* alternative faster version 

```{r}

install.packages(c("foreach", "doSNOW", "doParallel"))

library(foreach)
library(doParallel)
library(doSNOW)

# Set up the parallel backend
cl <- makeCluster(detectCores() - 1)  # use all cores but one
registerDoSNOW(cl)

# Initialize an empty list to hold the results
cosim_L6b <- list()

# Use foreach for parallel processing with %dopar% and add a progress bar
pb <- txtProgressBar(max = length(cosim_L6), style = 3)
progress <- function(n) setTxtProgressBar(pb, n)
opts <- list(progress = progress)
registerDoSNOW(makeCluster(detectCores(), outfile = "", options = opts))

cosim_L6b <- foreach(i = 1:length(cosim_L6), .packages = c("base", "stats")) %dopar% {
  
  cosim_L6b_i <- matrix(nrow = 0, ncol = 7)
  
  for (j in 1:5) {
    
    mat <- cosim_L6[[i]][j, , ]
   
    # Check the number of columns in the current matrix and base matrix
    num_cols_base <- 5
    num_cols_current <- ncol(mat)
    
    if (num_cols_base > num_cols_current) {
      # Add columns filled with NA to the current matrix
      mat <- cbind(mat, matrix(rep(NA, (num_cols_base - num_cols_current) * nrow(mat)), nrow=nrow(mat)))
    }
    
    cosim_L6b_i <- rbind(cosim_L6b_i, cbind(batch = i, n_in_batch = j, mat))
  }
  
  return(cosim_L6b_i)
}

close(pb)  # Close the progress bar

# Stop the cluster
stopCluster(cl)

# Combine the results from all parallel operations
cosim_L6b <- do.call(rbind, cosim_L6b)


```

### Calculate teh score in python
* for each item token I summed the five higest similarities. I then averaged the score by item

```{python}
import numpy as np
import pickle

with open("/Volumes/GoogleDrive/Meu Drive/colB5BERT/cosim_scores_L6.pkl", "rb") as file:
    item_by_posts_scores = pickle.load(file)
    

```

### Final item scores

```{r}
py$item_by_posts_scores

hist(py$item_by_posts_scores)

hist(data_L6_wide$BFI2_E_1)
hist(data_L6_wide$E_rec)

plot(data_L6_wide$BFI2_E_1, data_L6_wide$E_rec)


item_by_posts_scores <- py$item_by_posts_scores

rm(data_l6, chunks, file, cosim_L6, builtins, pickle)
length(item_by_posts_scores)

data_L6 <- tidyr::expand_grid(db_textos_splitted[ , c("id", "id_divisao")], coditem = base_itens$coditem)
data_L6$post_by_item_scores = item_by_posts_scores


```

### Correlations between colB5BERT and tests

```{r}
sjmisc::frq(base_itens$domain)
names(db_bfi)

col_names <- names(dplyr::select(db_bfi, acq_indx_ori:N_rec))

data_L6  <- data_L6  %>% 
 left_join(base_itens[ , c(2, 3, 6, 8)], by = "coditem")

data_L6  <- data_L6  %>% 
 left_join(db_bfi[ , c(1, 64:69)], by = "id") 
 
 names(data_L6)
 
 data_L6  <- data_L6  %>% 
   dplyr::select(-coditem) %>%
   dplyr::group_by(id, id_divisao, test, domain, pole) %>%
   dplyr::summarise(across(all_of(c("post_by_item_scores")), mean, na.rm=TRUE))


data_L6_wide <- data_L6 %>% 
 ungroup() %>%
 filter(!is.na(domain)) %>%
 pivot_wider(names_from = c(test, domain, pole), values_from = post_by_item_scores)


data_L6_wide_subj <- data_L6_wide %>% 
 group_by(id) %>%
 summarise(across(everything(), mean)) 

names(data_L6_wide)
psych::corr.test(data_L6_wide[ , 9:40], data_L6_wide[ , 3:8])

names(data_L6_wide_subj)

psych::corr.test(data_L6_wide_subj[ , 9:40], data_L6_wide_subj[ , 3:8])


data_L6_wide %>% ggplot(aes(y = BFI2_E_1 , x =E_rec)) + geom_point(alpha=1/2, color = "pink")

data_L6_wide_subj %>% ggplot(aes(y = BFI2_A_0 , x =O_rec)) + geom_point(alpha=1/2)

f <- as.formula( paste("O_rec=", paste(names(data_L6_wide_subj)[3:41], collapse = "+"), sep=""))

fit <- lm( O_rec ~ acq_indx_ori +  BFI2_A_0 + 
    BFI2_A_1 + BFI2_C_0 + BFI2_C_1 + BFI2_E_0 + BFI2_E_1 + BFI2_N_0 + 
    BFI2_N_1 + BFI2_O_0 + BFI2_O_1 +  OCDE_SEMS_A_0 + 
    OCDE_SEMS_A_1 + OCDE_SEMS_C_0 + OCDE_SEMS_C_1 + OCDE_SEMS_E_0 + 
    OCDE_SEMS_E_1 + OCDE_SEMS_M_0 + OCDE_SEMS_M_1 + OCDE_SEMS_N_0 + 
    OCDE_SEMS_N_1 + OCDE_SEMS_O_0 + OCDE_SEMS_O_1 + SENNA_A_0 + 
    SENNA_A_1 + SENNA_C_0 + SENNA_C_1 + SENNA_E_0 + SENNA_E_1 + 
    SENNA_N_0 + SENNA_N_1 + SENNA_O_0 + SENNA_O_1,  data_L6_wide_subj)
summary(fit)

sjPlot::tab_model(fit, std = TRUE)
```



### Miscelanea
```{r}
5*length(cosim_L6)
cbind(batch = 1, n_in_batch = 2, cosim_L6[[83]][2, , ])
length(cosim_L6[1:2])
typeof(cosim_L6[1:2])

rbind(cosim_L6[[1]][1, , ], cosim_L6[[2]][2, , ])


cosim_L6[[1]][2,,]

x <- cosim_L6[[1]]


new_array[1, , ]

swapp_3_to_1 <- function(x){
 
 # Initialize an empty array
 new_array <-  array(0, dim = c(5, 14, 5))
 old_array <- cosim_L6[[1]]
 
 # loop over first dimension of batches
 for (i in 1:5) {
  # loop over third dimension of five cosim
  for (j in 1:5) {
   new_array[j, , i] <- old_array[i, , j]
  }
  
 }
 
 return(new_array)
 
}
new_array[1, , ] 
ncol(cosim_L6[[1]][1, ,])

# first is the 

dim(cosim_L6[[1]])

length(cosim_L6) * 5

batch = c(rep(1, 5), rep(2, 5), rep(3, 5),  rep(4, 5), rep(5, 5))



# Let's assume 'names' is your vector of names, and 'values' is your vector of numbers
names <- c(...)  # replace with your data
values <- c(...)  # replace with your data

# Apply mean function to each group of values defined by names
averages <- tapply(values, names, mean)

```

